Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
some editing intro to sec 4

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS.  For this purpose, we first
provide the synthesiser's general architecture, followed by describing
two approaches that use it to automatically generate safe controllers:
the first one is a baseline approach which relies on a naive explicit
unwinding of the transition relation, whereas the second uses an
abstraction to implicitly evaluate all possible progressions of the
system simultaneously. % on an infinite time horizon.

>>>>

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS.  For this purpose, we first
provide the synthesiser's general architecture, followed by describing
our two approaches to synthesizing safe controllers:
the first one is a baseline approach which relies on a naive explicit
unwinding of the transition relation, whereas the second uses an
abstraction to implicitly evaluate all possible progressions of the
system simultaneously. % on an infinite time horizon.
